---
title: "analysis"
output:
  html_document: default
  pdf_document: default
  word_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(skimr)
source("R/utils.R")
```

# Load data

```{r, message=FALSE,warning=FALSE}
raw_data <- 
  read_csv("data/sm_patient_questionnarie_new.csv")
```

Variable names.

```{r}
colnames(raw_data)
```

Create unique ids for each participant.

```{r}
raw_data <- 
  raw_data %>% 
  mutate(participant_id = 1:577) %>% 
  select(participant_id, everything())
```

# Cleaning the dataset

Deleting duplicates.

```{r}
processed_data <- 
  raw_data %>% 
  filter(participant_id %ni% c(274, 462))
```

Lets see how many participants have missing data.

```{r}
skim(processed_data)
```

Filling up rows with empty input values.

```{r}
processed_data <-
  processed_data %>%
  mutate(
    not_sm_center = as.integer(not_sm_center),
    not_sm_center = replace_na(not_sm_center, 0L),
    not_sm_center = dplyr::case_when(
      sm_center_name == "nem járok neurológushoz" ~ 1L,
      TRUE ~ as.integer(not_sm_center)
    )
  )
```

Deleting participants not living in Hungary.

```{r}
not_in_hungary <- c(10, 30, 68, 71, 123, 125, 147, 249)

processed_data <- 
  processed_data %>% 
  filter(participant_id %ni% not_in_hungary)
```

Some respondents when asked about their SM center choose the other option and described the center in free text instead of choosing on of the pre-defined options. We replace these options with the pre-defined text so that we can analyse the SM centers prevalence.

```{r}
processed_data <-
  processed_data %>% 
  mutate(
    sm_center_name = case_when(
      participant_id == 446 ~ "Csolnoky Ferenc kórház, Veszprém",
      participant_id == 55 ~ "Szent-György kórház, Rendelőintézet, Székesfehérvár",
      participant_id == 44 ~ "Péterfy Sándor utcai kórház, Budapest",
      TRUE ~ sm_center_name
    )
  )
```

For the MRI data we had to change the free text responses in some cases. We also decided to drop the data in some cases we will also do that now.

```{r}
processed_data <-
  processed_data %>% 
  mutate(
    last_mri_changed = as.character(last_mri_changed),
    last_mri_drop = as.integer(last_mri_drop),
    last_mri = case_when(
      !is.na(last_mri_changed) ~ last_mri_changed,
      last_mri_drop == 1L ~ NA_character_,
      TRUE ~ last_mri
    ),
    last_mri = as.integer(last_mri)
  )
```

We would also like to extract the year of the completion of the survey.

```{r}
processed_data <-
  processed_data %>% 
  mutate(
    timestamp = as.character(timestamp),
    year_completition = str_sub(timestamp, 1, 4),
    year_completition = as.integer(year_completition),
    last_mri_time = year_completition - last_mri
    )
```

Note, that there are cases where the last time of the MRI was later than the completition of the survey, this have to be dropped.

# EDA

N all respondent.

```{r}
nrow(processed_data)
```

Sex count and percentage.

```{r}
count_and_prop(processed_data, sex)
```

Count patients treated in not SM center.

```{r}
count_and_prop(processed_data, not_sm_center)
```

Plot the same.

```{r}
plot_count_and_prop(processed_data, not_sm_center)
```

List unique SM centers in the data.

```{r}
processed_data %>% 
  filter(not_sm_center == 0L) %>% 
  distinct(sm_center_name)
```

Count the number of patients treated in each SM center.

```{r}
processed_data %>% 
  filter(not_sm_center == 0L) %>% 
  count_and_prop(sm_center_name)
```

Count how many patients do not have a neurologist.

```{r}
count_and_prop(processed_data, no_neurologist_care)
```

Age count and percentage.

```{r}
count_and_prop(processed_data, age)
```

Distance from the SM center.

```{r}
processed_data %>% 
  mutate(
    sm_center_distance_final = case_when(
      !is.na(sm_center_distance_drop) ~ NA_real_,
      !is.na(sm_center_distance_changed) ~ sm_center_distance_changed,
      is.na(sm_center_distance_changed) ~ as.numeric(str_extract(sm_center_distance, "\\d+"))),
    sm_center_distance_grouped = case_when(
      sm_center_distance_final < 10 ~ "Less than 10",
      sm_center_distance_final >= 10 & sm_center_distance_final <= 50 ~ "Between 10 and 50",
      sm_center_distance_final > 50 & sm_center_distance_final <= 100 ~ "Between 50 and 100",
      sm_center_distance_final > 100 ~ "More than 100",
      TRUE ~ NA_character_)
    ) %>%
  count_and_prop(sm_center_distance_grouped)
```

Number of patients who do not visit neurologist.

```{r}
processed_data %>% 
  count(no_neurologist_care)
```

Age of patients who do not visit neurologist.

```{r}
processed_data %>% 
  filter(no_neurologist_care == 1) %>% 
  count_and_prop(age)
```

Number of patients having problem with transportation by age group.

```{r}
processed_data %>% 
  count(transportation_problem, age) %>% 
  group_by(transportation_problem) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100)
```

Check whether patients who have problem with transportation use the patient transportation system.

```{r}
processed_data %>% 
  filter(transportation_problem == "igen") %>% 
  count_and_prop(use_patient_transportation)
```

Check how often do patients meet with their doctors. Only those who are in SM centers.

```{r}
processed_data %>% 
  filter(
    not_sm_center == 0L
    ) %>% 
  count_and_prop(doctor_visit)
```

Lets plot the results.

```{r}
processed_data %>% 
  filter(
    not_sm_center == 0L
    ) %>% 
  mutate(
    doctor_visit = case_when(
      doctor_visit == "3 havonta" ~ "Every 3 months",
      doctor_visit == "évente" ~ "Yearly",
      doctor_visit == "fél évente" ~ "Every 6 months",
      doctor_visit == "ritkábban" ~ "Less often",
      TRUE ~ NA_character_
    ),
    doctor_visit = as.factor(doctor_visit),
    doctor_visit = fct_relevel(doctor_visit, c("Every 3 months", "Every 6 months", "Yearly", "Less often"))
  ) %>% 
  plot_count_and_prop(
    doctor_visit,
    FALSE,
    x_title = "How often do patients meet with their neurologist?",
    limit_upper = 65,
    text_size = 12
    ) +
  theme(
    axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0, unit = "pt")),
    axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0, unit = "pt")),
    axis.title = element_text(size = 43),
    axis.text.x = element_text(margin = margin(t = 8, r = 0, b = 0, l = 0, unit = "pt")),
    axis.text = element_text(size = 33),
    axis.ticks = element_line(size = 1, color = 'black'),
    axis.line = element_line(size = 1)
  )
```

Lets see the same by age group.

```{r}
processed_data %>% 
  count(age, doctor_visit) %>% 
  group_by(age) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100) %>% 
  arrange(age, desc(n))
```

Lets see how many patients are part of a social organization for patients.

```{r}
processed_data %>% 
  count_and_prop(medical_group_membership)
```

Specifically for MSMBA.

```{r}
processed_data %>% 
  count_and_prop(heard_msmba)
```

Do patient who did not hear previously about MSMBA want to know more about this organization?

```{r}
processed_data %>% 
  filter(heard_msmba == "Nem") %>% 
  count_and_prop(msmba_more_info)
```

Specifically for MANIT.

```{r}
processed_data %>% 
  count_and_prop(heard_manit)
```

Lets see what do patients want to know more about.

```{r}
processed_data %>% 
  select(participant_id, age, education_interest_order) %>% 
  separate_rows(education_interest_order, sep = ";") %>% 
  count(age, education_interest_order) %>% 
  group_by(age) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100) %>% 
  arrange(age, desc(n)) %>% 
  group_by(age) %>%
  top_n(3)
```

Check whether patients prepare for consultation with their doctor.

```{r}
processed_data %>% 
  count_and_prop(prepare_consultation)
```

Lets see whether patients would be interested in getting funding for help if they had the opportunity.

```{r}
processed_data %>% 
  count_and_prop(funding)
```

Check whether patients use aid for walking.

```{r}
processed_data %>% 
  count_and_prop(walking_aid)
```

Same for age group.

```{r}
processed_data %>% 
  count(age, walking_aid) %>% 
  group_by(age) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100) %>% 
  arrange(age, desc(n))
```

Lets see if those who use a walking aid ever had financial problems in getting one.

```{r}
processed_data %>%
  filter(walking_aid == "Igen") %>% 
  count_and_prop(walking_aid_financial)
```

Lets see if they would be willing to buy walking aid.

```{r}
processed_data %>% 
  count_and_prop(used_walking_aid)
```

If they are a member in a social helping which group is it? Because it was a multiple choice question with a lot of categories it is not easy to present the results in an understandable format.

```{r}
# Number of participants with group membership
n_group_membership <- 
  processed_data %>% 
  filter(medical_group_membership == "Igen") %>% 
  nrow()

group_membership_sum_data <- 
  processed_data %>% 
  filter(medical_group_membership == "Igen") %>% 
  select(participant_id, which_medical_group) %>% 
  separate_rows(which_medical_group, sep = ";") %>% 
  mutate(
    group_simplified = case_when(
      which_medical_group %in% c("nyílt magyar facebook csoport", "zárt magyar facebook csoport (csak meghívóval csatlakozhat)") ~ "Hungarian FB group",
      which_medical_group %in% c("nyílt más nyelvű facebook csoport", "zárt más nyelvű facebook csoport (csak meghívóval csatlakozhat)") ~ "Non Hungarian FB group",
      which_medical_group == "Magyar Sclerosis Multiplexes Betegek Alapítványa" ~ "MSMBA",
      which_medical_group %in% c("egyéb", "egyéb zárt fórumok") ~ "Other",
      TRUE ~ NA_character_
    )
  ) %>%
  group_by(participant_id, group_simplified) %>% 
  summarize(n = n())
```

There were `r n_group_membership` participants who are part of any medical community groups. Out of these how many are part of at least one type of Hungarian FB group?

```{r}
group_membership_sum_data %>% 
  filter(group_simplified == "Hungarian FB group") %>%
  nrow()
```

How many of them are the part of MSMBA? As this was a multiple choice question there can be an overlap. It is possible to calculate the overlap but I do not think it is relevant.

```{r}
group_membership_sum_data %>% 
  filter(group_simplified == "MSMBA") %>%
  nrow()
```

Are they interested in further education regarding MS?

```{r}
processed_data %>% 
  count_and_prop(sm_education)
```

Same per age group.

```{r}
processed_data %>% 
  count(age, sm_education) %>% 
  group_by(age) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100) %>% 
  arrange(age, sm_education)
```

Did they use any other method for consultation then phone or meeting in person?

```{r}
processed_data %>% 
  count_and_prop(unusual_consultation_method)
```

Same per age group.

```{r}
processed_data %>% 
  count(age, unusual_consultation_method) %>% 
  group_by(age) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100) %>% 
  arrange(age, desc(n))
```

Which method did they use if they answered yes.

```{r}
processed_data %>% 
  filter(unusual_consultation_method == "igen") %>% 
  select(participant_id, unusual_consultation_method_description) %>% 
  separate_rows(unusual_consultation_method_description, sep = ";") %>% 
  count_and_prop(unusual_consultation_method_description)
```

Same for age group.

```{r}
processed_data %>% 
  filter(unusual_consultation_method == "igen") %>% 
  select(participant_id, age, unusual_consultation_method_description) %>% 
  separate_rows(unusual_consultation_method_description, sep = ";") %>% 
  count(age, unusual_consultation_method_description) %>% 
  group_by(age) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100) %>% 
  arrange(age, desc(n)) %>% 
  group_by(age) %>% 
  top_n(3)
```

Which further education method is prefered?

```{r}
processed_data %>% 
  select(participant_id, education_preferred_method) %>% 
  separate_rows(education_preferred_method, sep = ";") %>% 
  count_and_prop(education_preferred_method)
```

Same for age group.

```{r}
processed_data %>% 
  select(participant_id, age, education_preferred_method) %>% 
  separate_rows(education_preferred_method, sep = ";") %>% 
  count(age, education_preferred_method) %>% 
  group_by(age) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100) %>% 
  arrange(age, desc(n)) %>% 
  group_by(age) %>% 
  top_n(3)
```

Do they feel that their family understands their illness?

```{r}
processed_data %>% 
  count_and_prop(family_understanding)
```

Who can they depend on?

```{r}
processed_data %>% 
  select(participant_id, person_to_help) %>% 
  separate_rows(person_to_help, sep = ";") %>% 
  count_and_prop(person_to_help)
```

Same for age group.

```{r}
processed_data %>% 
  select(participant_id, age, person_to_help) %>% 
  separate_rows(person_to_help, sep = ";") %>% 
  count(age, person_to_help) %>% 
  group_by(age) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100) %>% 
  arrange(age, desc(n)) %>% 
  group_by(age) %>% 
  top_n(3)
```

Would they participate in MS education programs WITH their family?

```{r}
processed_data %>% 
  count_and_prop(sm_edcuation_children)
```

Is it possible for relatives to join the consultation with the doctor?

```{r}
processed_data %>% 
  count_and_prop(relative_consultation_option)
```

Do they want relatives to join?

```{r}
processed_data %>% 
  count_and_prop(relative_consultation_need)
```

Would they be willing to go to psychologist?

```{r}
processed_data %>% 
  count_and_prop(use_psychologist)
```

Same per age group.

```{r}
processed_data %>% 
  count(age, use_psychologist) %>% 
  group_by(age) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100) %>% 
  arrange(age, desc(n))
```

What are the main reasons behind NOT wanting to go to psychologist?

```{r}
processed_data %>% 
  filter(use_psychologist == "Nem") %>% 
  count_and_prop(use_psychologist_code) %>% 
  arrange(desc(n))
```

Main reasons behind wanting to go to a psychologist?

```{r}
processed_data %>% 
  filter(use_psychologist %in% c("Igen", "igen")) %>% 
  count_and_prop(use_psychologist_code) %>% 
  arrange(desc(n))
```

Do patients ask for hep from a physiotherapist?

```{r}
processed_data %>% 
  count_and_prop(use_physiotherapist)
```

What are the main reasons behind NOT asking for help?

```{r}
processed_data %>% 
  filter(use_physiotherapist == "Nem") %>% 
  count_and_prop(use_physiotherapist_code) %>% 
  arrange(desc(n))
```

Do they use rehabilitation?

```{r}
processed_data %>% 
  count_and_prop(use_rehabilitation)
```

What are the main reasons behind not using rehabilitation?

```{r}
processed_data %>% 
  filter(use_rehabilitation == "Nem") %>% 
  count_and_prop(use_rehabilitation_code) %>% 
  arrange(desc(n))
```

***

What are the most serious symptoms reported by the patients?

```{r}
processed_data %>% 
  count_and_prop(biggest_drawback_code) %>% 
  arrange(desc(n))
```

Do people who has bizonytalanság, pszichés, elfogadás, kognitív zavar as the biggest symptom go to psychological therapy?

```{r}
processed_data %>%
  mutate(symptom_type = case_when(biggest_drawback_code %in% c('bizonytalanság', 'pszichés', 'elfogadás', 'kognitív zavar') ~ "Psychological symptoms",
                                  biggest_drawback_code %ni% c('bizonytalanság', 'pszichés', 'elfogadás', 'kognitív zavar') ~ "Other symptoms",
                                  TRUE ~ NA_character_),
         use_psychologist = tolower(use_psychologist)) %>%
  count(symptom_type, use_psychologist) %>% 
  group_by(symptom_type) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100)
```

The proportion of patients with psychological symptoms.

```{r}
processed_data %>%
  mutate(symptom_type = case_when(biggest_drawback_code %in% c('bizonytalanság', 'pszichés', 'elfogadás', 'kognitív zavar') ~ "Psychological symptoms",
                                  biggest_drawback_code %ni% c('bizonytalanság', 'pszichés', 'elfogadás', 'kognitív zavar') ~ "Other symptoms",
                                  TRUE ~ NA_character_)) %>% 
  count_and_prop(symptom_type)
```

Why do patients with psychological symptoms do not go to psychologist?

```{r}
processed_data %>%
  mutate(symptom_type = case_when(biggest_drawback_code %in% c('bizonytalanság', 'pszichés', 'elfogadás', 'kognitív zavar') ~ "Psychological symptoms",
                                  biggest_drawback_code %ni% c('bizonytalanság', 'pszichés', 'elfogadás', 'kognitív zavar') ~ "Other symptoms",
                                  TRUE ~ NA_character_),
         use_psychologist = tolower(use_psychologist)) %>%
  filter(use_psychologist == "nem",
         symptom_type == "Psychological symptoms") %>% 
  count_and_prop(use_psychologist_code)
```

Same with plot.

```{r}
processed_data %>%
  mutate(symptom_type = case_when(biggest_drawback_code %in% c('bizonytalanság', 'pszichés', 'elfogadás', 'kognitív zavar') ~ "Psychological symptoms",
                                  biggest_drawback_code %ni% c('bizonytalanság', 'pszichés', 'elfogadás', 'kognitív zavar') ~ "Other symptoms",
                                  TRUE ~ NA_character_),
         use_psychologist = tolower(use_psychologist)) %>%
  filter(use_psychologist == "nem",
         symptom_type == "Psychological symptoms") %>%
  mutate(
    use_psychologist_code = case_when(
      use_psychologist_code == "nem elérhető a szolgáltatás" ~ "Service not available",
      use_psychologist_code == "nem értelmezhető" ~ "Irrelevant response",
      use_psychologist_code == "nincs bátorsága hozzá" ~ "Affraid to go",
      use_psychologist_code == "nincs pénze rá" ~ "Financial reasons",
      use_psychologist_code == "nincs szüksége rá" ~ "Not needed",
      TRUE ~ "Not responded"
    )
  ) %>% 
  count_and_prop(use_psychologist_code) %>% 
  ggplot() +
  aes(x = percentage, y = reorder(use_psychologist_code, n)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_x_continuous(expand = c(0, 0), limits = c(0, 60), labels = scales::label_percent(scale = 1)) +
  scale_y_discrete(expand = c(0, 0)) +
  labs(
    y = "Percieved reasons behind not\nseeing a psychologist by the patients",
    x = "Percentage"
  ) +
  theme_classic() +
  theme(
    legend.position = c(0.85, 0.8),
    plot.margin = margin(t = 0.5, l = 0.5, r = 0.5, b = 0.5, unit='cm')
  )
```

How big proportion of those who have mobilitás, fáradékonyság, egyensúlyzavar, fájdalom as main symptom goes to physical therapy?

```{r}
processed_data %>%
  mutate(symptom_type = case_when(biggest_drawback_code %in% c('mobilitás', 'fáradékonyság', 'egyensúlyzavar', 'fájdalom') ~ "Physiological symptoms",
                                  biggest_drawback_code %ni% c('mobilitás', 'fáradékonyság', 'egyensúlyzavar', 'fájdalom') ~ "Other symptoms",
                                  TRUE ~ NA_character_),
         use_physiotherapist = tolower(use_physiotherapist)) %>%
  count(symptom_type, use_physiotherapist) %>% 
  group_by(symptom_type) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100)
```

The same on a plot.

```{r}
processed_data %>%
  mutate(symptom_type = case_when(biggest_drawback_code %in% c('mobilitás', 'fáradékonyság', 'egyensúlyzavar', 'fájdalom', 'izomgörcsök', 'zsibbadás') ~ "Physical",
                                  biggest_drawback_code %ni% c('mobilitás', 'fáradékonyság', 'egyensúlyzavar', 'fájdalom', 'izomgörcsök', 'zsibbadás') ~ "Non-physical",
                                  TRUE ~ NA_character_),
         use_physiotherapist = tolower(use_physiotherapist),
         use_physiotherapist = case_when(
           use_physiotherapist == "igen" ~ "Yes",
           use_physiotherapist == "nem" ~ "No",
           TRUE ~ NA_character_
           )
         ) %>% 
  count(symptom_type, use_physiotherapist) %>% 
  group_by(symptom_type) %>% 
  mutate(
    n_all = sum(n),
    percentage = n / n_all * 100,
    text = paste0(n, "/", n_all)
    ) %>%
  ggplot() +
  aes(x = symptom_type, y = percentage, fill = use_physiotherapist) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = text, group = use_physiotherapist), position = position_dodge(width = 0.9), vjust = -0.5, size = 15) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 80), labels = scales::label_percent(scale = 1)) +
  labs(
    fill = "Does the patient go to physiotherapy?",
    y = "Percentage",
    x = "Main confounding symptom"
  ) +
  theme_classic() +
  theme(
    legend.position = c(0.85, 0.8),
    plot.margin = margin(t = 0.5, l = 0.5, r = 0.5, b = 0.5, unit = 'cm')
  )
```

Check whether patients who indicated that psychological and physical symptoms are their main confounding symptoms go to corresponding treatment options.

```{r}
plot_data_all <- 
  processed_data %>%
  mutate(symptom_type = case_when(biggest_drawback_code %in% c('mobilitás', 'fáradékonyság', 'egyensúlyzavar', 'fájdalom', 'izomgörcsök', 'zsibbadás') ~ "Physical",
                                  biggest_drawback_code %in% c('bizonytalanság', 'pszichés', 'elfogadás', 'kognitív zavar', 'izoláció') ~ "Psychological",
                                  TRUE ~ NA_character_),
         use_physiotherapist = tolower(use_physiotherapist),
         use_psychologist = tolower(use_psychologist),
         use_psychologist = case_when(
           use_psychologist == "igen" ~ "Yes",
           use_psychologist == "nem" ~ "No",
           TRUE ~ NA_character_
           ),
         use_physiotherapist = case_when(
           use_physiotherapist == "igen" ~ "Yes",
           use_physiotherapist == "nem" ~ "No",
           TRUE ~ NA_character_
           )
         ) %>% 
  filter(!is.na(symptom_type)) %>% 
  select(participant_id, symptom_type, use_physiotherapist, use_psychologist)

plot_data_physical <- 
  plot_data_all %>% 
  filter(symptom_type == "Physical") %>% 
  select(-use_psychologist) %>% 
  count(use_physiotherapist, symptom_type) %>% 
  mutate(
    n_all = sum(n),
    percentage = n / n_all * 100,
    text = paste0(n, "/", n_all)
    ) %>% 
  rename(use = use_physiotherapist)

plot_data_psychological <- 
  plot_data_all %>% 
  filter(symptom_type == "Psychological") %>% 
  select(-use_physiotherapist) %>% 
  count(use_psychologist, symptom_type) %>% 
  mutate(
    n_all = sum(n),
    percentage = n / n_all * 100,
    text = paste0(n, "/", n_all)
    ) %>% 
  rename(use = use_psychologist)

plot_data_merged <- bind_rows(
  plot_data_physical,
  plot_data_psychological
  )

plot_data_merged %>% 
  ggplot() +
  aes(x = symptom_type, y = percentage, fill = use) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = text, group = use), position = position_dodge(width = 0.9), vjust = -0.5, size = 15) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100), labels = scales::label_percent(scale = 1)) +
  scale_fill_manual(values=c("#8c1616", "grey35")) +
  labs(
    fill = "Does the patient\ngo to therapy?",
    y = "Percentage",
    x = "Main confunding symptom"
  ) +
  theme_classic() +
  theme(
    legend.position = c(0.85, 0.8),
    legend.title = element_text(size = 35),
    legend.text = element_text(size = 30),
    legend.background = element_rect(fill = "#b3cac7"),
    legend.key.size = unit(1, 'cm'),
    axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0, unit = "pt")),
    # axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0, unit = "pt")),
    axis.title = element_text(size = 45),
    # axis.text.x = element_text(margin = margin(t = 8, r = 0, b = 0, l = 0, unit = "pt")),
    axis.text = element_text(size = 35),
    axis.ticks = element_line(size = 1, color = 'black'),
    axis.line = element_line(size = 1, color = 'black'),
    plot.margin = margin(t = 1, l = 0.5, r = 0.5, b = 0.5, unit = 'cm'),
    panel.background = element_rect(fill = "#b3cac7"),
    plot.background = element_rect(fill = "#b3cac7")
  )
```

Do they go to rehabilitation?

```{r}
processed_data %>%
  mutate(symptom_type = case_when(biggest_drawback_code %in% c('mobilitás', 'fáradékonyság', 'egyensúlyzavar', 'fájdalom') ~ "Physiological symptoms",
                                  biggest_drawback_code %ni% c('mobilitás', 'fáradékonyság', 'egyensúlyzavar', 'fájdalom') ~ "Other symptoms",
                                  TRUE ~ NA_character_),
         use_rehabilitation = tolower(use_rehabilitation)) %>%
  count(symptom_type, use_rehabilitation) %>% 
  group_by(symptom_type) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100)
```

Do patients with mobilitás, egyensúlyzavar problems use walking aids?

```{r}
processed_data %>%
  mutate(symptom_type = case_when(biggest_drawback_code %in% c('mobilitás', 'egyensúlyzavar') ~ "Physiological symptoms",
                                  biggest_drawback_code %ni% c('mobilitás', 'egyensúlyzavar') ~ "Other symptoms",
                                  TRUE ~ NA_character_),
         walking_aid = tolower(walking_aid)) %>%
  count(symptom_type, walking_aid) %>% 
  group_by(symptom_type) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100)
```

Educational interest.

```{r}
edu_interest_all <- 
  processed_data %>%
  select(participant_id, education_interest_order) %>% 
  separate_rows(education_interest_order, sep = ";")

edu_interest_options <- 
  edu_interest_all %>% 
  count(education_interest_order) %>% 
  arrange(desc(n)) %>% 
  slice_head(n = 23) %>% 
  pull(education_interest_order)

# filter only options that were present in the survey
edu_interest_filtered <- 
  edu_interest_all %>% 
  dplyr::filter(education_interest_order %in% edu_interest_options)

edu_interest_n <- 
  edu_interest_filtered %>% 
  distinct(participant_id) %>% 
  nrow()

edu_interest_filtered %>% 
  count(education_interest_order) %>% 
  arrange(desc(n)) %>% 
  mutate(n_patients = edu_interest_n,
         percentage_patients = n / n_patients * 100)
```

How many patients had an MRI lately?

```{r}
processed_data %>% 
  filter(
    last_mri_time >= 0,
    not_sm_center == 0L
    ) %>% 
  count_and_prop(last_mri_time)
```
