---
title: "analysis"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(skimr)
source("R/utils.R")
```

# Load data

```{r, message=FALSE,warning=FALSE}
raw_data <- 
  read_csv("data/sm_patient_questionnarie.csv")
```

Variable names.

```{r}
colnames(raw_data)
```

Create unique ids for each participant.

```{r}
raw_data <- 
  raw_data %>% 
  mutate(participant_id = 1:577) %>% 
  select(participant_id, everything())
```

# Cleaning the dataset

Deleting duplicates.

```{r}
processed_data <- 
  raw_data %>% 
  filter(participant_id %ni% c(274, 462))
```

Lets see how many participants have missing data.

```{r}
skim(processed_data)
```

Deleting participants with missing data.

```{r}
# processed_data <- 
#   processed_data %>% 
#   filter(participant_id != 348)
```

Filling up rows with empty input values.

```{r}
processed_data <-
  processed_data %>%
  mutate(not_sm_center = case_when(is.na(not_sm_center) ~ 0L,
                                   TRUE ~ 1L))
```

Deleting participants not living in Hungary.

```{r}
not_in_hungary <- c(10, 30, 68, 71, 123, 125, 147, 249)

processed_data <- 
  processed_data %>% 
  filter(participant_id %ni% not_in_hungary)
```

# EDA

N all respondent.

```{r}
nrow(processed_data)
```

Sex count and percentage.

```{r}
count_and_prop(processed_data, sex)
```

Count patients treated in not SM center.

```{r}
count_and_prop(processed_data, not_sm_center)
```

Plot the same.

```{r}
plot_count_and_prop(processed_data, not_sm_center)
```

Count how many patients do not have a neurologist.

```{r}
count_and_prop(processed_data, no_neurologist_care)
```

Age count and percentage.

```{r}
count_and_prop(processed_data, age)
```

Distance from the SM center.

```{r}
processed_data %>% 
  mutate(
    sm_center_distance_final = case_when(
      !is.na(sm_center_distance_drop) ~ NA_real_,
      !is.na(sm_center_distance_changed) ~ sm_center_distance_changed,
      is.na(sm_center_distance_changed) ~ as.numeric(str_extract(sm_center_distance, "\\d+"))),
    sm_center_distance_grouped = case_when(
      sm_center_distance_final < 10 ~ "Less than 10",
      sm_center_distance_final >= 10 & sm_center_distance_final <= 50 ~ "Between 10 and 50",
      sm_center_distance_final > 50 & sm_center_distance_final <= 100 ~ "Between 50 and 100",
      sm_center_distance_final > 100 ~ "More than 100",
      TRUE ~ NA_character_)
    ) %>%
  count_and_prop(sm_center_distance_grouped)
```

Number of patients who do not visit neurologist.

```{r}
processed_data %>% 
  count(no_neurologist_care)
```

Age of patients who do not visit neurologist.

```{r}
processed_data %>% 
  filter(no_neurologist_care == 1) %>% 
  count_and_prop(age)
```

Number of patients having problem with transportation by age group.

```{r}
processed_data %>% 
  count(transportation_problem, age) %>% 
  group_by(transportation_problem) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100)
```

Check whether patients who have problem with transportation use the patient transportation system.

```{r}
processed_data %>% 
  filter(transportation_problem == "igen") %>% 
  count_and_prop(use_patient_transportation)
```

Check how often do patients meet with their doctors.

```{r}
processed_data %>% 
  count_and_prop(doctor_visit)
```

Lets see the same by age group.

```{r}
processed_data %>% 
  count(age, doctor_visit) %>% 
  group_by(age) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100) %>% 
  arrange(age, desc(n))
```

Lets see how many patients are part of a social organization for patients.

```{r}
processed_data %>% 
  count_and_prop(medical_group_membership)
```

Specifically for MSMBA.

```{r}
processed_data %>% 
  count_and_prop(heard_msmba)
```

Do patient who did not hear previously about MSMBA want to know more about this organization?

```{r}
processed_data %>% 
  filter(heard_msmba == "Nem") %>% 
  count_and_prop(msmba_more_info)
```

Specifically for MANIT.

```{r}
processed_data %>% 
  count_and_prop(heard_manit)
```

Lets see what do patients want to know more about.

```{r}
processed_data %>% 
  select(participant_id, age, education_interest_order) %>% 
  separate_rows(education_interest_order, sep = ";") %>% 
  count(age, education_interest_order) %>% 
  group_by(age) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100) %>% 
  arrange(age, desc(n)) %>% 
  group_by(age) %>% 
  top_n(3)
```

Check whether patients prepare for consultation with their doctor.

```{r}
processed_data %>% 
  count_and_prop(prepare_consultation)
```

Lets see whether patients would be interested in getting funding for help if they had the opportunity.

```{r}
processed_data %>% 
  count_and_prop(funding)
```

Check whether patients use aid for walking.

```{r}
processed_data %>% 
  count_and_prop(walking_aid)
```

Same for age group.

```{r}
processed_data %>% 
  count(age, walking_aid) %>% 
  group_by(age) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100) %>% 
  arrange(age, desc(n))
```

Lets see if those who use a walking aid ever had financial problems in getting one.

```{r}
processed_data %>%
  filter(walking_aid == "Igen") %>% 
  count_and_prop(walking_aid_financial)
```

Lets see if they would be willing to buy walking aid.

```{r}
processed_data %>% 
  count_and_prop(used_walking_aid)
```

If they are a member in a social helping which group is it?

```{r}
processed_data %>% 
  filter(medical_group_membership == "Igen") %>% 
  count_and_prop(which_medical_group) %>% 
  arrange(desc(n))
```

Are they interested in further education regarding MS?

```{r}
processed_data %>% 
  count_and_prop(sm_education)
```

Same per age group.

```{r}
processed_data %>% 
  count(age, sm_education) %>% 
  group_by(age) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100) %>% 
  arrange(age, sm_education)
```

Did they use any other method for consultation then phone or meeting in person?

```{r}
processed_data %>% 
  count_and_prop(unusual_consultation_method)
```

Same per age group.

```{r}
processed_data %>% 
  count(age, unusual_consultation_method) %>% 
  group_by(age) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100) %>% 
  arrange(age, desc(n))
```

Which method did they use if they answered yes.

```{r}
processed_data %>% 
  filter(unusual_consultation_method == "igen") %>% 
  select(participant_id, unusual_consultation_method_description) %>% 
  separate_rows(unusual_consultation_method_description, sep = ";") %>% 
  count_and_prop(unusual_consultation_method_description)
```

Same for age group.

```{r}
processed_data %>% 
  filter(unusual_consultation_method == "igen") %>% 
  select(participant_id, age, unusual_consultation_method_description) %>% 
  separate_rows(unusual_consultation_method_description, sep = ";") %>% 
  count(age, unusual_consultation_method_description) %>% 
  group_by(age) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100) %>% 
  arrange(age, desc(n)) %>% 
  group_by(age) %>% 
  top_n(3)
```

Which further education method is prefered?

```{r}
processed_data %>% 
  select(participant_id, education_preferred_method) %>% 
  separate_rows(education_preferred_method, sep = ";") %>% 
  count_and_prop(education_preferred_method)
```

Same for age group.

```{r}
processed_data %>% 
  select(participant_id, age, education_preferred_method) %>% 
  separate_rows(education_preferred_method, sep = ";") %>% 
  count(age, education_preferred_method) %>% 
  group_by(age) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100) %>% 
  arrange(age, desc(n)) %>% 
  group_by(age) %>% 
  top_n(3)
```

Do they feel that their family understands their illness?

```{r}
processed_data %>% 
  count_and_prop(family_understanding)
```

Who can they depend on?

```{r}
processed_data %>% 
  select(participant_id, person_to_help) %>% 
  separate_rows(person_to_help, sep = ";") %>% 
  count_and_prop(person_to_help)
```

Same for age group.

```{r}
processed_data %>% 
  select(participant_id, age, person_to_help) %>% 
  separate_rows(person_to_help, sep = ";") %>% 
  count(age, person_to_help) %>% 
  group_by(age) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100) %>% 
  arrange(age, desc(n)) %>% 
  group_by(age) %>% 
  top_n(3)
```

Would they participate in MS education programs WITH their family?

```{r}
processed_data %>% 
  count_and_prop(sm_edcuation_children)
```

Is it possible for relatives to join the consultation with the doctor?

```{r}
processed_data %>% 
  count_and_prop(relative_consultation_option)
```

Do they want relatives to join?

```{r}
processed_data %>% 
  count_and_prop(relative_consultation_need)
```

Would they be willing to go to psychologist?

```{r}
processed_data %>% 
  count_and_prop(use_psychologist)
```

Same per age group.

```{r}
processed_data %>% 
  count(age, use_psychologist) %>% 
  group_by(age) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100) %>% 
  arrange(age, desc(n))
```

What are the main reasons behind NOT wanting to go to psychologist?

```{r}
processed_data %>% 
  filter(use_psychologist == "Nem") %>% 
  count_and_prop(use_psychologist_code) %>% 
  arrange(desc(n))
```

Main reasons behind wanting to go to a psychologist?

```{r}
processed_data %>% 
  filter(use_psychologist %in% c("Igen", "igen")) %>% 
  count_and_prop(use_psychologist_code) %>% 
  arrange(desc(n))
```

Do patients ask for hep from a physiotherapist?

```{r}
processed_data %>% 
  count_and_prop(use_physiotherapist)
```

What are the main reasons behind NOT asking for help?

```{r}
processed_data %>% 
  filter(use_physiotherapist == "Nem") %>% 
  count_and_prop(use_physiotherapist_code) %>% 
  arrange(desc(n))
```

Do they use rehabilitation?

```{r}
processed_data %>% 
  count_and_prop(use_rehabilitation)
```

What are the main reasons behind not using rehabilitation?

```{r}
processed_data %>% 
  filter(use_rehabilitation == "Nem") %>% 
  count_and_prop(use_rehabilitation_code) %>% 
  arrange(desc(n))
```

***

What are the most serious symptoms reported by the patients?

```{r}
processed_data %>% 
  count_and_prop(biggest_drawback_code) %>% 
  arrange(desc(n))
```

Do people who has bizonytalanság, pszichés, elfogadás, kognitív zavar as the biggest symptom go to psychological therapy?

```{r}
processed_data %>%
  mutate(symptom_type = case_when(biggest_drawback_code %in% c('bizonytalanság', 'pszichés', 'elfogadás', 'kognitív zavar') ~ "Psychological symptoms",
                                  biggest_drawback_code %ni% c('bizonytalanság', 'pszichés', 'elfogadás', 'kognitív zavar') ~ "Other symptoms",
                                  TRUE ~ NA_character_),
         use_psychologist = tolower(use_psychologist)) %>%
  count(symptom_type, use_psychologist) %>% 
  group_by(symptom_type) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100)
```

The proportion of patients with psychological symptomps.

```{r}
processed_data %>%
  mutate(symptom_type = case_when(biggest_drawback_code %in% c('bizonytalanság', 'pszichés', 'elfogadás', 'kognitív zavar') ~ "Psychological symptoms",
                                  biggest_drawback_code %ni% c('bizonytalanság', 'pszichés', 'elfogadás', 'kognitív zavar') ~ "Other symptoms",
                                  TRUE ~ NA_character_)) %>% 
  count_and_prop(symptom_type)
```

Why do patients with psychological symptoms do not go to psychologist?

```{r}
processed_data %>%
  mutate(symptom_type = case_when(biggest_drawback_code %in% c('bizonytalanság', 'pszichés', 'elfogadás', 'kognitív zavar') ~ "Psychological symptoms",
                                  biggest_drawback_code %ni% c('bizonytalanság', 'pszichés', 'elfogadás', 'kognitív zavar') ~ "Other symptoms",
                                  TRUE ~ NA_character_),
         use_psychologist = tolower(use_psychologist)) %>%
  filter(use_psychologist == "nem",
         symptom_type == "Psychological symptoms") %>% 
  count_and_prop(use_psychologist_code)
```

How big proportion of those who have mobilitás, fáradékonyság, egyensúlyzavar, fájdalom as main symptom goes to physical therapy?

```{r}
processed_data %>%
  mutate(symptom_type = case_when(biggest_drawback_code %in% c('mobilitás', 'fáradékonyság', 'egyensúlyzavar', 'fájdalom') ~ "Physiological symptoms",
                                  biggest_drawback_code %ni% c('mobilitás', 'fáradékonyság', 'egyensúlyzavar', 'fájdalom') ~ "Other symptoms",
                                  TRUE ~ NA_character_),
         use_physiotherapist = tolower(use_physiotherapist)) %>%
  count(symptom_type, use_physiotherapist) %>% 
  group_by(symptom_type) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100)
```

Do they go to rehabilitation?

```{r}
processed_data %>%
  mutate(symptom_type = case_when(biggest_drawback_code %in% c('mobilitás', 'fáradékonyság', 'egyensúlyzavar', 'fájdalom') ~ "Physiological symptoms",
                                  biggest_drawback_code %ni% c('mobilitás', 'fáradékonyság', 'egyensúlyzavar', 'fájdalom') ~ "Other symptoms",
                                  TRUE ~ NA_character_),
         use_rehabilitation = tolower(use_rehabilitation)) %>%
  count(symptom_type, use_rehabilitation) %>% 
  group_by(symptom_type) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100)
```

Do patients with mobilitás, egyensúlyzavar problems use walking aids?

```{r}
processed_data %>%
  mutate(symptom_type = case_when(biggest_drawback_code %in% c('mobilitás', 'egyensúlyzavar') ~ "Physiological symptoms",
                                  biggest_drawback_code %ni% c('mobilitás', 'egyensúlyzavar') ~ "Other symptoms",
                                  TRUE ~ NA_character_),
         walking_aid = tolower(walking_aid)) %>%
  count(symptom_type, walking_aid) %>% 
  group_by(symptom_type) %>% 
  mutate(n_all = sum(n),
         percentage = n / n_all * 100)
```

Educational interest.

```{r}
edu_interest_all <- 
  processed_data %>%
  select(participant_id, education_interest_order) %>% 
  separate_rows(education_interest_order, sep = ";")

edu_interest_options <- 
  edu_interest_all %>% 
  count(education_interest_order) %>% 
  arrange(desc(n)) %>% 
  slice_head(n = 23) %>% 
  pull(education_interest_order)

# filter only options that were present in the survey
edu_interest_filtered <- 
  edu_interest_all %>% 
  dplyr::filter(education_interest_order %in% edu_interest_options)

edu_interest_n <- 
  edu_interest_filtered %>% 
  distinct(participant_id) %>% 
  nrow()

edu_interest_filtered %>% 
  count(education_interest_order) %>% 
  arrange(desc(n)) %>% 
  mutate(n_patients = edu_interest_n,
         percentage_patients = n / n_patients * 100)
```

How many patients had an MRI lately?

